### 2020-10-28 smoothing.tex
more questions

JD: Yes, but you need units. $\tau = 1 \mathrm{day}$ is exactly what I meant by a time scale of 1 day.

>>>>

JD: Yes, but you need units. $\tau = 1 \mathrm{day}$ is exactly what I meant by a time scale of 1 day. 
AG: Sorry, I am not sure here about the units.

(4) $\sigma$ is the testing rate with unit of 1/time. $\sigma$ has two limits
(i) When $W \approx N0$;
If we assume that $\tau \gg \rho$, $\sigma=\rho \frac{\tau N0}{(\tau+\rho)N_0} \approx \rho \frac{\tau N0}{(\tau)N_0} = \rho$.

(ii) When $W \approx 0$;
$\sigma \approx \tau$.

(5) Right now there are no restictions on the weights, $W_S, W_I$ and $W_R$. These are representing different testing strategies. For example if $W_S=W_I=W_R$, it represents the random testing from the whole population with no tracing.
(i) Does it make sense $W_S+W_I+W_R=1$? thus if we increase the W_I, the other two weights will decrease.
(ii) I am thinking of somehow connect $W_*$ and testing rate of the whole population $\rho$. With the new definition of the $\sigma$ that JD suggested above, this is already incorporated in the rate of testing but not in the testing strategies.
